---
title: "p8105_hw1_yd2865"
author: "Yan Duan"
date: "2025-09-16"
output: github_document
---

```{r setup, include=FALSE}
Sys.setlocale("LC_TIME", "English_United States")
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
library(moderndive)
library(tidyverse)
library(ggplot2)
```

I'm an R Markdown document! 


# Problem 0.1:
  This is a public GitHub repo with an R Project and includes a single `.Rmd` file that renders to `github_document`. 
  
# Problem 0.2:
  This repo focuses on clear variable names, readable and well-indented code, explanatory text for results. 
  
  
```{r load data}
# Load early_january_weather dataset

data("early_january_weather")
```


  
# Problem 1:

Assign the dataset `early_january_weather` to a new object named `weather_df` to facilitate subsequent plotting and analysis.

```{r}
weather_df <- early_january_weather
```

* This dataset records hourly weather observations, including variables such as temperature (`temp`), time (`time_hour`), and humidity (`humid`). 
* The dataset has `r nrow(weather_df)` rows and `r ncol(weather_df)` columns. The average temperature is approximately `r round(mean(weather_df$temp, na.rm = TRUE), 2)` °F.


```{r}
# Use ggplot2 to draw a scatter plot.

ggplot(weather_df, aes(x = time_hour, y = temp, color = humid)) + 
  geom_point(alpha = 0.8) +
  labs(
    x = "Time (hourly)",
    y = "Temperature (°F)",
    color = "Humidity",
    title = "Temperature vs Time"
  )
```

From the scatter plot, it can be seen that within the time period of the data recording, the temperature gradually increased over time. 

Meanwhile, the change in humidity is shown through the color of the points, when the humidity is high, the color is lighter, and when the humidity is low, the color is darker. 

It indicates that the distribution of temperature and humidity over time has a distinct pattern.



```{r}
# Export the scatterplot to my project directory 

ggsave("Temperature vs Time.jpg",
  width = 7, height = 6, dpi = 300)
```


